A Novel Approach to Supervised Classification Using Non-Linear Metrics

### 2017-01-03 icml2017/paper.tex
Add

@@

\begin{abstract} 
Clustering (also known as unsupervised classification) and Classification (commonly understood to be supervised,
 i.e. based on training data) are common ways of performing data analysis to achieve a range of objectives like 
anomaly detection and diagnosis, data segmentation and model development/refinement. Consequently, there is a 
large body of research on these topics (see for example\cite{Hastie} and references therein for a survey of 
currently used methods) offering different solutions ranging from K-means, spectral methods and other more 
complex methods for Clustering, and Support Vector Machines (SVM), Artificial(Deep/Shallow) Neural Networks (ANN), their 
non-linear Kernel-based variants and others for Classification.

@@

Finally, the metric learning process can be formulated as an optimization problem (Mixed-Integer Linear Program, or MILP, 
in its simplest form) that can be hard to solve for realistic data sizes, but we present fast and parallelizable methods to compute the optimal metric.
We demonstrate classification and computational performance of the algorithms through several simple and intuitive examples.
\end{abstract}

@@

\paragraph{Contributions.}

\section{Motivation}

\section{Illustration Examples}

>>>>

\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
% 
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

@@

\begin{abstract}

\end{abstract}

\section{Introduction}

\todo[inline,color=red]{This is original abstract,
however, abstract should be just a few lines}

Clustering (also known as unsupervised classification) and Classification (commonly understood to be supervised,
 i.e. based on training data) are common ways of performing data analysis to achieve a range of objectives like 
anomaly detection and diagnosis, data segmentation and model development/refinement. Consequently, there is a 
large body of research on these topics (see for example\cite{Hastie} and references therein for a survey of 
currently used methods) offering different solutions ranging from K-means, spectral methods and other more 
complex methods for Clustering, and Support Vector Machines (SVM), Artificial(Deep/Shallow) Neural Networks (ANN), their 
non-linear Kernel-based variants and others for Classification.

@@

Finally, the metric learning process can be formulated as an optimization problem (Mixed-Integer Linear Program, or MILP, 
in its simplest form) that can be hard to solve for realistic data sizes, but we present fast and parallelizable methods to compute the optimal metric.
We demonstrate classification and computational performance of the algorithms through several simple and intuitive examples.

@@

\todo[inline,color=green]{Explain very clearly what we want to do and why it is important.

mention

-clustering

-better NN search

-outlier detection

-where to sample new data

}

\paragraph{Brief Literature Review.}

\cite{weinberger2005distance}

\cite{xing2003distance}

\cite{weinberger2009distance}

\cite{yang2006efficient}

\cite{ying2012distance}

\cite{schultz2004learning}

\cite{rosales2006learning}

\paragraph{Our Contributions.}

\section{Motivation \& Illustration Examples}
